Determinism, Complexity, and Predictability in Computer Performance

### 2014-02-27 concl.tex

>>>>

Moved the following material here from the results section, since
they're more general.  But there's a lot of repeated material that
will obviously need to get compressed and streamlined.

Just because there is forward information transfer, that does not mean
that an arbitrary predictor can interpret or utilize it, but WPE can
tell us when this structure is present.

These results support that time series with low to moderate complexity
($0\le WPE \le 0.85$) can be predicted more efficiently than a na\"ive
random walk \emph{and} that complexity can be qualitatively measured
for a real-valued noisy time series using WPE. This will allow
practitioners to stop spinning their wheels in the case of signals who
are simply better predicted with a simple strategy like random
walk. The analysis of these results illuminates an interesting point:
The way structure, information and complexity are processed by a
generating process plays a crucial role in the success of a given
prediction scheme.

As we discussed in Section \ref{sec:meaComplex} distinguishing
structured from unstructured complexity in the case of real-valued
time series is non trivial, i.e., distinguishing when a complex signal
omits predictable structure and when the signal is effectively random
is not a trivial task. As described in Section \ref{sec:intro}, for a
practitioner this can be frustrating because it can be nearly
impossible to find the source of faulty predictions: Is it simply that
we need to use a more ideal (possibly more advanced) predictor or is
it the case that the time series is simply so complex that using a
simple (yet inconsistent) forecast strategy such as random walk is the
best we can do. Fortunately, weighted permutation entropy (WPE) allows
us to make this distinction for noisy real-valued time series.

Needs to be more stuff in the WPE section for this to tie back to as
well as in the new related work section.  [[Joshua, can you elaborate
    on this so that Ryan can fill this in?]]
